### 2013-09-20 intro.tex
updated / new Kirema content

Kirema's intro text will go here.

>>>>

Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer related
death.~\cite{Howlander2011} Screening with prostate specific antigen (PSA) and
digital rectal examination (DRE) has led to earlier PCa detection but
performance of these measures is not optimal, leading to imprecise risk
assessment.  In addition, the random nature of transrectal ultrasonography
(TRUS) guided biopsies can miss or underestimate the burden of
cancer.~\cite{Gupta2013} Earlier disease diagnosis leads to challenges in
deciding optimal management strategies for patients presenting with fewer
disease burden, whereas missed tumors on TRUS-guided biopsies can result in
inappropriate diagnoses.

The use of non-invasive imaging in the evaluation of PCa could lead to improved
diagnosis, risk-stratification, and management. Magnetic resonance imaging
(MRI) has been available for use in the workup of patients with PCa since the
early 1980s but early studies on its diagnostic accuracy were heterogeneous.
However, the more recent ability to include functional parameters in PCa MRI
analysis has yielded promising results.~\cite{Gupta2013,Hricak2007} Among the
MRI modalities currently used in the study of PCa, it is well established that
T2-weighted imaging (T2WI) offers the best assessment of prostate anatomy due
to its ability to delineate prostatic margins, distinguish internal structures
and differentiate among the glandular zones.

Acoustic radiation force impulse (ARFI) imaging is an ultrasound-based modality
that evaluates the mechanical properties of tissues.~\cite{Nightingale2002}
ARFI imaging has the potential to aid in PCa diagnosis and management by
evaluating the structural composition of prostate zones and tumors base on
their stiffness.  Zhai et al were able to visualize prostatic anatomy by
utilizing ARFI imaging \exvivo. In a second study, Zhai et al. demonstrated the
feasibility of ARFI prostate imaging \inviv\invivo.~\cite{Zhai2012}  However, to the authors’ best
knowledge, there have been no studies to date that compare \invivo ARFI
prostate imaging to other imaging modalities.~\cite{Zhai2010} The goal of this
study was to evaluate the ability of ARFI to distinguish prostate zonal anatomy
\invivo as compared to endorectal T2WI.
